\def \correo{Email}
\def \tel{Cellphone}

\def \resumen{Profesional Summary}
\def \resumenTexto{Professional with over 15 years of experience in software development, 
passionate about technology and the adoption of best practices. 
Key skills include Agile methodologies, backend and frontend development, 
functional programming, NoSQL databases, AWS, Podman/Docker, and Linux. 
Extensive experience in the Fintech sector and also in various other industries.}


\def \techSkills{Technical Skills Summary}
\def \databases{Databases}
\def \buildtools{Build Tools}
\def \env{Environments}
\def \lenguage{Languages}
\def \lengText{Native Spanish, Technical and Business English, Basic Japanese}
\def \other{Other}

\def \exp{Experience}

\def \japan{Tokyo, Japan}
\def \softDevSeniorScala{Scala Senior Software Developer}
\def \paidyText{
  \begin{itemize}
    \item Developed new features for the payment system, including integration with コンビニ (convenience stores).
    \item Implemented integration with SMBC銀行 (SMBC Bank) to enable automatic monthly debits.
    \item Designed and implemented integration components using Rust.
  \end{itemize}
}

\def \gorillaTitle{Senior Software Developer in Scala and Java}
\def \gorillaText{
  \begin{itemize}
    \item Worked on projects for various clients and industries, developing incident 
    management software and stock market investment software.
    \item Implemented investment logic using the Julia programming language.
  \end{itemize}
}

\def \cirisTitle{Owner, Chief Executive Officer, Developer, Architect, and DevOps Specialist}
\def \cirisText{
  \begin{itemize}
    \item Founded and managed a business with over 10 employees, serving both national and international clients.
    \item Delivered custom software development services using Node.js and JavaScript.
    \item Oversaw all aspects of business management, including sales, client acquisition, and customer relationship management.
    \item Acted as the technical leader, responsible for DevOps and team training.
  \end{itemize}
}

\def \gbsysTitle{Java Software Developer}
\def \gbsysText{
  \begin{itemize}
    \item Developed an electronic voting system for the University of Costa Rica (UCR).
    \item Designed and implemented a procurement management system for the UCR.
  \end{itemize}
}

\def \educacion{Education}
\def \licenciaturaTitle{Bachelor’s degree in Computer Software Engineering}
\def \licenciaturaText{
  \begin{itemize}
    \item Five years of university education in total.
  \end{itemize}
}
\def \bachilleratorTitle{Associate's degree in Computer Software Engineering}
\def \bachilleratorText{
  \begin{itemize}
    \item Three years of university education in total.
    \item Magna Cum Laude
  \end{itemize}
}

\def \desarrolloProfesional{Professional Development}

\def \elfinanciero{Featured in "40 Under 40" by El Financiero newspaper.}
\input{cv.tex}
